Bricking up backdoors in Intrusion Detection Systems

### 2019-09-12 paper/paper.tex
Fixed a few references

In addition to this problems, for the training of models, usually datasets are used which have been generated artificially in a controlled test environment. As a downside of this approach, it is unclear whether a \gls{ml} model learns to classify based on characteristics that are inherent to the attacks which should be detected, or rather learns to classify based on patterns that were unintentionally created during dataset generation.

>>>>

In addition to these problems, for the training of models, usually datasets are used which have been generated artificially in a controlled test environment. As a downside of this approach, it is unclear whether a \gls{ml} model learns to classify based on characteristics that are inherent to the attacks which should be detected, or rather learns to classify based on patterns that were unintentionally created during dataset generation.
